EGGs are adhesive!

### 2025-03-13 calco/main.tex
Update main.tex

\begin{corollary}\label{cor:ereg}
	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\hyp$. 
\end{corollary}

@@

\begin{corollary}\label{cor:rege}
		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and onlu if $I(h)$ is a regular mono in $\hyp$. 
\end{corollary}

>>>>

\begin{corollary}\label{cor:ereg}
	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\EqHyp$. 
\end{corollary}

@@

\begin{corollary}\label{cor:rege}
		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\EqHyp$. 
\end{corollary}
